Exploiting the Social Graph: Increasing Engagement via Collaborative Interactive Evolution

### 2017-02-08 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
bib folder created
True authors and reduced to 8 pages

\author{\IEEEauthorblockN{Michael Shell}
\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
Georgia Institute of Technology}
\and
\IEEEauthorblockN{Homer Simpson}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: homer@thesimpsons.com}
\and
\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
\IEEEauthorblockA{Starfleet Academy\\
San Francisco, California 96678--2391}}

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_2.png}
    \caption{User network view of the Base deployment}
    \label{fig:B-network}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_3.png}
    \caption{User network view of the Graph Gamification deployment}
    \label{fig:GG-network}
\end{figure}
\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.5in]{img/comparison.png}
    \caption{Users ranked by the number of phenotypes they rated vs. the number of phenotypes evaluated using a logarithmic scale. } % Explain a little more and label axes. The
                         % three lines have the same label,
                         % "participation". Not too clear - JJ
                         % Done - Mario
    \label{fig:top-ranked-participation}
\end{figure*}

@@

\section*{Acknowledgment}
Space reserved for Acknowledgment text, Lorem ipsum dolor sit amet, consectetur adipiscing elit,
sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis 
nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.

@@

\bibliographystyle{IEEEtran}
\bibliography{evospace-i,volunteer,biblio,geneura}

>>>>

\author{\IEEEauthorblockN{Mario García-Valdez, Amaury Hernández Águila, Alejandra Mancilla}
\IEEEauthorblockA{Instituto Tecnológico de Tijuana\\
Tijuana, Mexico\\
Email: (mario,amherag)@tectijuana.edu.mx,
amherag@tectijuana.edu.mx,alejandra.mancilla@gmail.com}
\and
\IEEEauthorblockN{Juan Julián Merelo Guervós}
\IEEEauthorblockA{Universidad de Granada, CITIC\\
Email: jmerelo@geneura.ugr.es}
}

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_2.png}
    \caption{User network view of the Base deployment}
    \label{fig:B-network}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_3.png}
    \caption{User network view of the Graph Gamification deployment}
    \label{fig:GG-network}
\end{figure}
\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.3in]{img/comparison.png}
    \caption{Users ranked by the number of phenotypes they rated vs. the number of phenotypes evaluated using a logarithmic scale. } % Explain a little more and label axes. The
                         % three lines have the same label,
                         % "participation". Not too clear - JJ
                         % Done - Mario
    \label{fig:top-ranked-participation}
\end{figure*}

@@

\section*{Acknowledgment}
Space reserved for Acknowledgment text

@@

\bibliographystyle{IEEEtran}
\bibliography{../bib/evospace-i,../bib/volunteer,../bib/biblio,../bib/geneura}
